---
title: "Figure 5 acdf, Figure 6 cd, Sup Figure 9b"
author: "Mehdi Karimi"
date: "30/04/2020"
output: 
  html_document:
    code_folding: hide
    highlight: zenburn
    number_sections: yes
    theme: yeti
    toc: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dyno)
library(tidyverse)
library(velocyto.R)
library(DESeq2)
library("Matrix")
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ggpubr))
library(gam)
library(splatter)
library(slingshot)
library(DT)
library(Seurat)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(scater)
library(scran)
library(knitr)
library(org.Mm.eg.db)
library(cluster)
library(dynamicTreeCut)
library(SCORPIUS)
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ggpubr))
suppressPackageStartupMessages(library(magrittr))
suppressPackageStartupMessages(library(metaMA))
suppressPackageStartupMessages(library(DT))
library(VennDiagram)
library("jpeg")
library("tiff")
library(ggplot2)
library(cowplot)
library(gridExtra)
library(knitr)
library(kableExtra)
```


```{r,echo=T, eval=T, cache=T, message=F, warning=FALSE, fig.width=5, fig.height=5}

####################
# Loading rep2 data
####################

ldat_new <- read.loom.matrices("/Volumes/bioinfomatics$/Mehdi/Matthias/scRNA-seq/scRNAseq_CRG_02012020/onefilepercell_HFWL7BBXY_1_IDT-DUI-NXT-66_and_others_0VWWZ.loom")

ldat_new <- lapply(ldat_new,function(x) {
  colnames(x) <-  gsub(".bam","",gsub("onefilepercell_HFWL7BBXY_1_IDT-DUI-NXT-66_and_others_0VWWZ:","",colnames(x)))
  x
})

meta_data <- read.csv(file="/Volumes/bioinfomatics$/Mehdi/Matthias/scRNA-seq/scRNAseq_CRG_02012020/sample_info.csv", header=TRUE, sep=",")
rownames(meta_data) <- meta_data$sample_ID
meta_data$rep <- 'rep2'
meta_data <- meta_data[,c('rep','sample_label')]
colnames(meta_data) <- c('rep','celltype')
meta_data$celltype <- gsub('TCRint_DP_WT','TCRhiDP',gsub('CD8_SP_TCRpos_WT','CD8SP',gsub("CD4_SP_WT","CD4SP",gsub("CD4_pos_8lo_WT","CD4+8low",gsub("CD69_pos_DP_WT","CD69posDP",gsub("CD69_neg_DP_WT","CD69negDP",meta_data$celltype))))))


meta_data$celltype <- gsub('TCRint_DP_MHCclassII_KO','TCRhiDP_C2KO',gsub('CD8_SP_TCRpos_MHCclassII_KO','CD8SP_C2KO',gsub("CD4_SP_MHCclassII_KO","CD4SP_C2KO",gsub("CD4_pos_8lo_classII_KO","CD4+8low_C2KO",gsub("CD69_pos_DP_MHCclassII_KO","CD69posDP_C2KO",gsub("CD69_neg_DP_MHCclassII_KO","CD69negDP_C2KO",meta_data$celltype))))))

meta_data <- meta_data[!(rownames(meta_data)=="HFWL7BBXY_1_IDT-DUI-NXT-49" | rownames(meta_data)=="HFWL7BBXY_1_IDT-DUI-NXT-333"),]
meta_data[grep('C2KO',meta_data$celltype),]$rep <- 'rep2_KO'
meta_data$celltype <- gsub('_C2KO','', meta_data$celltype)

# exonic read (spliced) expression matrix
emat_rep2 <- ldat_new$spliced
emat_rep2 <- emat_rep2[, colnames(emat_rep2) %in% as.vector(rownames(meta_data))];


# intronic read (unspliced) expression matrix
nmat_rep2 <- ldat_new$unspliced
nmat_rep2 <- nmat_rep2[, colnames(nmat_rep2) %in% as.vector(rownames(meta_data))];

# spanning read (intron+exon) expression matrix
smat_rep2 <- ldat_new$spanning;
smat_rep2 <- smat_rep2[, colnames(smat_rep2) %in% as.vector(rownames(meta_data))];


######################
# Loading rep1 data
######################

ldat <- read.loom.matrices("/Volumes/bioinfomatics$/Mehdi/Matthias/scRNA-seq/onefilepercell_P2221_N707-S505_and_others_96WOS.loom")

ldat <- lapply(ldat,function(x) {
  colnames(x) <-  gsub(".bam","",gsub(".*:","",colnames(x)))
  x
})

WishBone_tsne <- read.csv(file="/Volumes/bioinfomatics$/Mehdi/Matthias/scRNA-seq/WishBone_tsne_with_highTCR.csv", header=TRUE, sep=",")
colnames(WishBone_tsne) <- c('CellName','x','y','Sample')

colData <- read.csv(file="/Volumes/bioinfomatics$/Mehdi/Matthias/scRNA-seq/colData.csv", header=TRUE, sep=",")

merged_meta1 <- merge(x = WishBone_tsne, y = colData, by = "CellName")
color_dt <- data.frame(Sample.x=c('WT1','WT2','WT3','WT4','WT5','highTCR_Rest'), color=c('#f44e42','#ffac38','#bcff37','#36eeff','#9335ff','#36ffee'))
merged_meta <- merge(x = merged_meta1, y = color_dt, by = "Sample.x")
merged_meta <- merged_meta[,c('CellCode','Sample.x')]
rownames(merged_meta) <- merged_meta$CellCode
merged_meta$rep <- 'rep1'
merged_meta <- merged_meta[,c('rep','Sample.x')]
colnames(merged_meta) <- c('rep','celltype')
merged_meta$celltype <- gsub('highTCR_Rest','TCRhiDP',gsub('WT5','CD8SP',gsub("WT4","CD4SP",gsub("WT3","CD4+8low",gsub("WT2","CD69posDP",gsub("WT1","CD69negDP",merged_meta$celltype))))))

# exonic read (spliced) expression matrix
emat_rep1 <- ldat$spliced
colnames(emat_rep1) <- gsub("-","_",colnames(emat_rep1))
emat_rep1 <- emat_rep1[, colnames(emat_rep1) %in% as.vector(rownames(merged_meta))];


# intronic read (unspliced) expression matrix
nmat_rep1 <- ldat$unspliced
colnames(nmat_rep1) <- gsub("-","_",colnames(nmat_rep1))
nmat_rep1 <- nmat_rep1[, colnames(nmat_rep1) %in% as.vector(rownames(merged_meta))];

# spanning read (intron+exon) expression matrix
smat_rep1 <- ldat$spanning;
colnames(smat_rep1) <- gsub("-","_",colnames(smat_rep1))
smat_rep1 <- smat_rep1[, colnames(smat_rep1) %in% as.vector(rownames(merged_meta))];


############
#merging rep1 & rep2
############

emat <- cbind(emat_rep1,emat_rep2)
nmat <- cbind(nmat_rep1,nmat_rep2)
smat <- cbind(smat_rep1,smat_rep2)
meta_info <- rbind(merged_meta,meta_data)


###########
# Running Seurat 
###########

WT_Thymocye <- CreateSeuratObject(emat, meta.data = meta_info)
WT_Thymocye.list <- SplitObject(WT_Thymocye, split.by = "rep")

for (i in 1:length(WT_Thymocye.list)) {
    WT_Thymocye.list[[i]] <- NormalizeData(WT_Thymocye.list[[i]], verbose = FALSE)
    WT_Thymocye.list[[i]] <- FindVariableFeatures(WT_Thymocye.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}

Rep1_log <- t(GetAssayData(WT_Thymocye.list[[1]],slot='data',assay = "RNA"))
Rep2_log <- t(GetAssayData(WT_Thymocye.list[[3]],slot='data',assay = "RNA"))
Rep2KO_log <- t(GetAssayData(WT_Thymocye.list[[2]],slot='data',assay = "RNA"))

meta_info$x1 <- 'Others'
meta_info$x2 <- 'Others'
meta_info$x3 <- 'Others'
meta_info$x4 <- 'Others'
meta_info$x5 <- 'Cd8-'
meta_info$x6 <- 'Cd4-'
meta_info$x7 <- 'Itm2a-'
meta_info$x8 <- 'Stat1-'

meta_info$x9 <- 'Others'
meta_info$x10 <- 'Others'
meta_info$x11 <- 'Others'
meta_info$x12 <- 'Others'

colnames(meta_info) <- c("rep", "celltype", "Cd4+Cd8+","Cd4+Cd8-", "Cd4-Cd8+", "Cd4-Cd8-", 'Cd8', 'Cd4', 'Itm2a', 'Stat1', "Zbtb7b+Runx3+","Zbtb7b+Runx3-", "Zbtb7b-Runx3+", "Zbtb7b-Runx3-") 


meta_info[rownames(Rep1_log[Rep1_log[,'Zbtb7b'] > 0.1 & Rep1_log[,'Runx3'] > 0.1,]),'Zbtb7b+Runx3+'] <- 'Zbtb7b+Runx3+'
meta_info[rownames(Rep2_log[Rep2_log[,'Zbtb7b'] > 0.1 & Rep2_log[,'Runx3'] > 0.1,]),'Zbtb7b+Runx3+'] <- 'Zbtb7b+Runx3+'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Zbtb7b'] > 0.1 & Rep2KO_log[,'Runx3'] > 0.1,]),'Zbtb7b+Runx3+'] <- 'Zbtb7b+Runx3+'

meta_info[rownames(Rep1_log[Rep1_log[,'Zbtb7b'] > 0.1 & Rep1_log[,'Runx3'] < 0.1,]),'Zbtb7b+Runx3-'] <- 'Zbtb7b+Runx3-'
meta_info[rownames(Rep2_log[Rep2_log[,'Zbtb7b'] > 0.1 & Rep2_log[,'Runx3'] < 0.1,]),'Zbtb7b+Runx3-'] <- 'Zbtb7b+Runx3-'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Zbtb7b'] > 0.1 & Rep2KO_log[,'Runx3'] < 0.1,]),'Zbtb7b+Runx3-'] <- 'Zbtb7b+Runx3-'

meta_info[rownames(Rep1_log[Rep1_log[,'Zbtb7b'] < 0.1 & Rep1_log[,'Runx3'] > 0.1,]),'Zbtb7b-Runx3+'] <- 'Zbtb7b-Runx3+'
meta_info[rownames(Rep2_log[Rep2_log[,'Zbtb7b'] < 0.1 & Rep2_log[,'Runx3'] > 0.1,]),'Zbtb7b-Runx3+'] <- 'Zbtb7b-Runx3+'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Zbtb7b'] < 0.1 & Rep2KO_log[,'Runx3'] > 0.1,]),'Zbtb7b-Runx3+'] <- 'Zbtb7b-Runx3+'

meta_info[rownames(Rep1_log[Rep1_log[,'Zbtb7b'] < 0.1 & Rep1_log[,'Runx3'] < 0.1,]),'Zbtb7b-Runx3-'] <- 'Zbtb7b-Runx3-'
meta_info[rownames(Rep2_log[Rep2_log[,'Zbtb7b'] < 0.1 & Rep2_log[,'Runx3'] < 0.1,]),'Zbtb7b-Runx3-'] <- 'Zbtb7b-Runx3-'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Zbtb7b'] < 0.1 & Rep2KO_log[,'Runx3'] < 0.1,]),'Zbtb7b-Runx3-'] <- 'Zbtb7b-Runx3-'


meta_info[rownames(Rep1_log[Rep1_log[,'Cd4'] > 0.1 & Rep1_log[,'Cd8a'] > 0.1,]),'Cd4+Cd8+'] <- 'Cd4+Cd8+'
meta_info[rownames(Rep2_log[Rep2_log[,'Cd4'] > 0.1 & Rep2_log[,'Cd8a'] > 0.1,]),'Cd4+Cd8+'] <- 'Cd4+Cd8+'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Cd4'] > 0.1 & Rep2KO_log[,'Cd8a'] > 0.1,]),'Cd4+Cd8+'] <- 'Cd4+Cd8+'

meta_info[rownames(Rep1_log[Rep1_log[,'Cd4'] > 0.1 & Rep1_log[,'Cd8a'] < 0.1,]),'Cd4+Cd8-'] <- 'Cd4+Cd8-'
meta_info[rownames(Rep2_log[Rep2_log[,'Cd4'] > 0.1 & Rep2_log[,'Cd8a'] < 0.1,]),'Cd4+Cd8-'] <- 'Cd4+Cd8-'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Cd4'] > 0.1 & Rep2KO_log[,'Cd8a'] < 0.1,]),'Cd4+Cd8-'] <- 'Cd4+Cd8-'

meta_info[rownames(Rep1_log[Rep1_log[,'Cd4'] < 0.1 & Rep1_log[,'Cd8a'] > 0.1,]),'Cd4-Cd8+'] <- 'Cd4-Cd8+'
meta_info[rownames(Rep2_log[Rep2_log[,'Cd4'] < 0.1 & Rep2_log[,'Cd8a'] > 0.1,]),'Cd4-Cd8+'] <- 'Cd4-Cd8+'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Cd4'] < 0.1 & Rep2KO_log[,'Cd8a'] > 0.1,]),'Cd4-Cd8+'] <- 'Cd4-Cd8+'

meta_info[rownames(Rep1_log[Rep1_log[,'Cd4'] < 0.1 & Rep1_log[,'Cd8a'] < 0.1,]),'Cd4-Cd8-'] <- 'Cd4-Cd8-'
meta_info[rownames(Rep2_log[Rep2_log[,'Cd4'] < 0.1 & Rep2_log[,'Cd8a'] < 0.1,]),'Cd4-Cd8-'] <- 'Cd4-Cd8-'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Cd4'] < 0.1 & Rep2KO_log[,'Cd8a'] < 0.1,]),'Cd4-Cd8-'] <- 'Cd4-Cd8-'

meta_info[rownames(Rep1_log[Rep1_log[,'Cd8a'] > 0.1,]),'Cd8'] <- 'Cd8+'
meta_info[rownames(Rep2_log[Rep2_log[,'Cd8a'] > 0.1,]),'Cd8'] <- 'Cd8+'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Cd8a'] > 0.1,]),'Cd8'] <- 'Cd8+'

meta_info[rownames(Rep1_log[Rep1_log[,'Cd4'] > 0.1,]),'Cd4'] <- 'Cd4+'
meta_info[rownames(Rep2_log[Rep2_log[,'Cd4'] > 0.1,]),'Cd4'] <- 'Cd4+'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Cd4'] > 0.1,]),'Cd4'] <- 'Cd4+'

meta_info[rownames(Rep1_log[Rep1_log[,'Itm2a'] > 0.5,]),'Itm2a'] <- 'Itm2a+'
meta_info[rownames(Rep2_log[Rep2_log[,'Itm2a'] > 0.5,]),'Itm2a'] <- 'Itm2a+'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Itm2a'] > 0.1,]),'Itm2a'] <- 'Itm2a+'

meta_info[rownames(Rep1_log[Rep1_log[,'Stat1'] > 0.2,]),'Stat1'] <- 'Stat1+'
meta_info[rownames(Rep2_log[Rep2_log[,'Stat1'] > 0.2,]),'Stat1'] <- 'Stat1+'
meta_info[rownames(Rep2KO_log[Rep2KO_log[,'Stat1'] > 0.1,]),'Stat1'] <- 'Stat1+'

meta_info[meta_info$celltype=='CD4SP' & meta_info$Itm2a=='Itm2a+' & meta_info$Stat1=='Stat1-', 'celltype'] <- 'CD4SP_Immature'
meta_info[meta_info$celltype=='CD4SP' & (meta_info$Itm2a=='Itm2a-' | meta_info$Stat1=='Stat1+'), 'celltype'] <- 'CD4SP_Mature'


WT_Thymocye <- CreateSeuratObject(emat, meta.data = meta_info)
WT_Thymocye.list <- SplitObject(WT_Thymocye, split.by = "rep")

for (i in 1:length(WT_Thymocye.list)) {
    WT_Thymocye.list[[i]] <- NormalizeData(WT_Thymocye.list[[i]], verbose = FALSE)
    WT_Thymocye.list[[i]] <- FindVariableFeatures(WT_Thymocye.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}

meta_info <- WT_Thymocye@meta.data

reference.list <- WT_Thymocye.list[c("rep1", "rep2","rep2_KO")]
WT_Thymocye.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30)

WT_Thymocye.integrated <- IntegrateData(anchorset = WT_Thymocye.anchors, dims = 1:30)

DefaultAssay(WT_Thymocye.integrated) <- "integrated"

# Run the standard workflow for visualization and clustering
WT_Thymocye.integrated <- ScaleData(WT_Thymocye.integrated, verbose = FALSE)
WT_Thymocye.integrated <- RunPCA(WT_Thymocye.integrated, npcs = 30, verbose = FALSE)
WT_Thymocye.integrated <- RunUMAP(WT_Thymocye.integrated, reduction = "pca", dims = 1:30)

gene_set <- read.csv(file="/Volumes/bioinfomatics$/Mehdi/Matthias/scRNA-seq/scRNAseq_CRG_02012020/gene_set/DE_gene_drodeRes_rep2_fset.csv", header=FALSE, sep=",")

emat <- cbind(emat_rep1,emat_rep2)
nmat <- cbind(nmat_rep1,nmat_rep2)
smat <- cbind(smat_rep1,smat_rep2)
# meta_info <- rbind(merged_meta,meta_data)

emat <- emat[intersect(gene_set$V1,rownames(emat)),]
emat <- emat[!(rownames(emat) =='Cd4' | rownames(emat) == 'Cd8a' | rownames(emat) =='Cd8b1'),]

###########
#Running Seurat 
###########

WT_Thymocye <- CreateSeuratObject(emat, meta.data = meta_info)
WT_Thymocye.list <- SplitObject(WT_Thymocye, split.by = "rep")

for (i in 1:length(WT_Thymocye.list)) {
    WT_Thymocye.list[[i]] <- NormalizeData(WT_Thymocye.list[[i]], verbose = FALSE)
    WT_Thymocye.list[[i]] <- FindVariableFeatures(WT_Thymocye.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}

reference.list <- WT_Thymocye.list[c("rep1", "rep2","rep2_KO")]
WT_Thymocye.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30)

WT_Thymocye.integrated <- IntegrateData(anchorset = WT_Thymocye.anchors, dims = 1:30)

# switch to integrated assay. The variable features of this assay are automatically
# set during IntegrateData

DefaultAssay(WT_Thymocye.integrated) <- "integrated"

# Run the standard workflow for visualization and clustering
WT_Thymocye.integrated <- ScaleData(WT_Thymocye.integrated, verbose = FALSE)
WT_Thymocye.integrated <- RunPCA(WT_Thymocye.integrated, npcs = 30, verbose = FALSE)
WT_Thymocye.integrated <- RunUMAP(WT_Thymocye.integrated, reduction = "pca", dims = 1:30)

# Filtering cells with too many or too few cells

Rep1_filtered_rep2 <- subset(WT_Thymocye.integrated, cells = rownames(meta_info[meta_info$rep=='rep1' |
         (meta_info$rep=='rep2_KO' & meta_info$celltype=='CD69posDP' & meta_info$nCount_RNA < 1500000 & meta_info$nCount_RNA > 750000) |
         (meta_info$rep=='rep2_KO' & meta_info$celltype!='CD69posDP' & meta_info$nCount_RNA < 1500000 & meta_info$nCount_RNA > 500000) |
         (meta_info$rep=='rep2' & meta_info$celltype=='CD69posDP' & meta_info$nCount_RNA < 1500000 & meta_info$nCount_RNA > 750000) |
         (meta_info$rep=='rep2' & meta_info$celltype!='CD69posDP' & meta_info$nCount_RNA < 1500000 & meta_info$nCount_RNA > 500000) 
                ,]))


# Dividing CD4SP to CD4SP Immature and Mature

meta_info_new <- Rep1_filtered_rep2@meta.data
PCA <- as.data.frame(Rep1_filtered_rep2@reductions$pca@cell.embeddings)
rownames(PCA) <-  rownames(Rep1_filtered_rep2@reductions$pca@cell.embeddings)

meta_info_new$PC_1 <- PCA$PC_1
meta_info_new$PC_2 <- PCA$PC_2
meta_info_new$PC_3 <- PCA$PC_3

meta_info_new[meta_info_new$celltype=='CD4+8low' & meta_info_new$PC_2 < meta_info_new$PC_1,'celltype'] <- 'CD4SP_Immature'

meta_info[rownames(meta_info_new),'celltype'] <- meta_info_new$celltype
```


```{r,echo=T, eval=T, cache=T, message=F, warning=FALSE, fig.width=16, fig.height=7}

gene_set <- read.csv(file="/Volumes/bioinfomatics$/Mehdi/Matthias/scRNA-seq/scRNAseq_CRG_02012020/gene_set/DE_gene_drodeRes_rep2_fset.csv", header=FALSE, sep=",")

emat <- cbind(emat_rep1,emat_rep2)
nmat <- cbind(nmat_rep1,nmat_rep2)
smat <- cbind(smat_rep1,smat_rep2)

emat <- emat[intersect(gene_set$V1,rownames(emat)),]
emat <- emat[!(rownames(emat) =='Cd4' | rownames(emat) == 'Cd8a' | rownames(emat) =='Cd8b1'),]


###########
#Running Seurat 
###########

WT_Thymocye <- CreateSeuratObject(emat, meta.data = meta_info)
WT_Thymocye.list <- SplitObject(WT_Thymocye, split.by = "rep")

for (i in 1:length(WT_Thymocye.list)) {
    WT_Thymocye.list[[i]] <- NormalizeData(WT_Thymocye.list[[i]], verbose = FALSE)
    WT_Thymocye.list[[i]] <- FindVariableFeatures(WT_Thymocye.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = FALSE)
}

reference.list <- WT_Thymocye.list[c("rep1", "rep2", "rep2_KO")]
WT_Thymocye.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30)

WT_Thymocye.integrated <- IntegrateData(anchorset = WT_Thymocye.anchors, dims = 1:30)


library(ggplot2)
library(cowplot)
# switch to integrated assay. The variable features of this assay are automatically
# set during IntegrateData
DefaultAssay(WT_Thymocye.integrated) <- "integrated"

# Run the standard workflow for visualization and clustering
WT_Thymocye.integrated <- ScaleData(WT_Thymocye.integrated, verbose = FALSE)
WT_Thymocye.integrated <- RunPCA(WT_Thymocye.integrated, npcs = 30, verbose = FALSE)
WT_Thymocye.integrated <- RunUMAP(WT_Thymocye.integrated, reduction = "pca", dims = 1:30)

PCA <- as.data.frame(WT_Thymocye.integrated@reductions$pca@cell.embeddings)



# Original runing 
emat <- cbind(emat_rep1,emat_rep2)
nmat <- cbind(nmat_rep1,nmat_rep2)
smat <- cbind(smat_rep1,smat_rep2)

###########
#Running Seurat 
###########

WT_Thymocye <- CreateSeuratObject(emat, meta.data = meta_info)
WT_Thymocye.list <- SplitObject(WT_Thymocye, split.by = "rep")

for (i in 1:length(WT_Thymocye.list)) {
    WT_Thymocye.list[[i]] <- NormalizeData(WT_Thymocye.list[[i]], verbose = FALSE)
    WT_Thymocye.list[[i]] <- FindVariableFeatures(WT_Thymocye.list[[i]], selection.method = "vst", 
        nfeatures = 5000, verbose = FALSE)
}

reference.list <- WT_Thymocye.list[c("rep1", "rep2", "rep2_KO")]
WT_Thymocye.anchors <- FindIntegrationAnchors(object.list = reference.list, dims = 1:30)

WT_Thymocye.integrated <- IntegrateData(anchorset = WT_Thymocye.anchors, dims = 1:30)


# switch to integrated assay. The variable features of this assay are automatically
# set during IntegrateData
DefaultAssay(WT_Thymocye.integrated) <- "integrated"

WT_Thymocye.integrated <- ScaleData(WT_Thymocye.integrated, verbose = FALSE)
WT_Thymocye.integrated <- RunPCA(WT_Thymocye.integrated, npcs = 30, verbose = FALSE)
WT_Thymocye.integrated <- RunUMAP(WT_Thymocye.integrated, reduction = "pca", dims = 1:30)


WT_Thymocye.integrated@reductions$pca@cell.embeddings <-  as.matrix(PCA)

draw_Plots <-  function(data_scatter_new, meta_data_f, gene_name){

  
  meta_data_f <- cbind(meta_data_f, as.data.frame(data_scatter_new[,gene_name]))
  meta_data_f <- meta_data_f[c(-8,-9)]
  colnames(meta_data_f)[13] <- gene_name
  meta_data_f$celltype <- factor(meta_data_f$celltype, levels=c("CD8SP", "CD4SP_Mature", "Sel_Intermed_Cd4-Cd8+", "Sel_Intermed_Cd4+Cd8-", "Sel_Intermed_Cd4+Cd8+", "CD69negDP"))
  
if(gene_name=="H2-K1"){
 colnames(meta_data_f)[13] <- "H2K1"
 gene_name <- "H2K1"}

if(gene_name=="H2-D1"){
 colnames(meta_data_f)[13] <- "H2D1"
 gene_name <- "H2D1"}
      

P1 <- ggbarplot(meta_data_f, x = "celltype", y = gene_name, 
          add = "mean_se",
          fill = "celltype", palette = c("blue", "green", "red", "darkturquoise", "black", "darkgray"),
          position = position_dodge(0.8))+
    theme_classic()+ylab(paste0(gene_name," Expression"))+
  theme(text = element_text(size = 16, face = "bold"))+
  theme(axis.text = element_text(size = 16, face = "bold"))+
  theme(plot.title = element_text(size = 16,face = "bold"))+ coord_flip()
  
print(P1)

  }


####

Rep1_filtered_rep2 <- subset(WT_Thymocye.integrated, cells = rownames(meta_info[meta_info$celltype != "CD4SP_Immature" &
         ((meta_info$rep=='rep2' & meta_info$celltype=='CD69posDP' & meta_info$nCount_RNA < 1500000 & meta_info$nCount_RNA > 750000) |
         (meta_info$rep=='rep2' & meta_info$celltype!='CD69posDP' & meta_info$nCount_RNA < 1500000 & meta_info$nCount_RNA > 500000)) 
                ,]))

Rep1_filtered_rep2 <- subset(Rep1_filtered_rep2, cells = rownames(meta_info[
           !((meta_info$celltype=="CD69posDP" | meta_info$celltype=="TCRhiDP" | meta_info$celltype=="CD4+8low") & meta_info$Cd4=="Cd4-" & meta_info$Cd8=="Cd8-") 
                ,]))


Rep1_filtered_rep2@meta.data[((Rep1_filtered_rep2@meta.data$celltype=="CD69posDP" | Rep1_filtered_rep2@meta.data$celltype=="TCRhiDP" | Rep1_filtered_rep2@meta.data$celltype=="CD4+8low") & Rep1_filtered_rep2@meta.data$Cd4=="Cd4+" & Rep1_filtered_rep2@meta.data$Cd8=="Cd8+"), 'celltype'] <- "Sel_Intermed_Cd4+Cd8+"

Rep1_filtered_rep2@meta.data[((Rep1_filtered_rep2@meta.data$celltype=="CD69posDP" | Rep1_filtered_rep2@meta.data$celltype=="TCRhiDP" | Rep1_filtered_rep2@meta.data$celltype=="CD4+8low") & Rep1_filtered_rep2@meta.data$Cd4=="Cd4+" & Rep1_filtered_rep2@meta.data$Cd8=="Cd8-"), 'celltype'] <- "Sel_Intermed_Cd4+Cd8-"

Rep1_filtered_rep2@meta.data[((Rep1_filtered_rep2@meta.data$celltype=="CD69posDP" | Rep1_filtered_rep2@meta.data$celltype=="TCRhiDP" | Rep1_filtered_rep2@meta.data$celltype=="CD4+8low") & Rep1_filtered_rep2@meta.data$Cd4=="Cd4-" & Rep1_filtered_rep2@meta.data$Cd8=="Cd8+"), 'celltype'] <- "Sel_Intermed_Cd4-Cd8+"

DefaultAssay(Rep1_filtered_rep2) <- "RNA"
data_scatter <- as.data.frame(t(GetAssayData(Rep1_filtered_rep2,slot='data',assay = "RNA")))
meta_data_new <- Rep1_filtered_rep2@meta.data
meta_data_new$PC_1 <- 0
meta_data_new$PC_1 <- Rep1_filtered_rep2@reductions$pca@cell.embeddings[rownames(meta_data_new),'PC_1']

meta_data_new$Cd4Cd8 <- "NA"
meta_data_new$Cd4Cd8 <- paste0(meta_data_new$Cd4, meta_data_new$Cd8)

meta_data_new$PC1_range <- "-10_to_-5"
meta_data_new[meta_data_new$PC_1 > -5 & meta_data_new$PC_1 < -2.5, "PC1_range" ] <- "-5_to_-2.5"
meta_data_new[meta_data_new$PC_1 > -2.5 & meta_data_new$PC_1 < 0, "PC1_range" ] <- "-2.5_to_0"
meta_data_new[meta_data_new$PC_1 > 0 & meta_data_new$PC_1 < 2.5, "PC1_range" ] <- "0_to_2.5"
meta_data_new[meta_data_new$PC_1 > 2.5 & meta_data_new$PC_1 < 7.5, "PC1_range" ] <- "2.5_to_7.5"



```

## Figure5.a) Mean expression of CD4 lineage markers by selection intermediates of the indicated co-receptor status.

```{r,echo=T, eval=T, cache=T, message=F, warning=FALSE, fig.width=16, fig.height=7}
draw_Plots(data_scatter, meta_data_new, 'Cd4')
draw_Plots(data_scatter, meta_data_new, 'Zbtb7b')
draw_Plots(data_scatter, meta_data_new, 'Cd40lg')

```

## Figure5.c) Mean expression of CD8 lineage markers by selection intermediates of the indicated co-receptor status.

```{r,echo=T, eval=T, cache=T, message=F, warning=FALSE, fig.width=16, fig.height=7}

draw_Plots(data_scatter, meta_data_new, 'Cd8a')
draw_Plots(data_scatter, meta_data_new, 'Runx3')
draw_Plots(data_scatter, meta_data_new, 'Nkg7')
draw_Plots(data_scatter, meta_data_new, 'Itgae')
```

## Figure5.d) Mean expression of TCR activation genes by selection intermediates of the indicated co-receptor status.


```{r,echo=T, eval=T, cache=T, message=F, warning=FALSE, fig.width=16, fig.height=7}

draw_Plots(data_scatter, meta_data_new, 'Cd69')
draw_Plots(data_scatter, meta_data_new, 'Egr1')
draw_Plots(data_scatter, meta_data_new, 'Nr4a1')
draw_Plots(data_scatter, meta_data_new, 'Itm2a')
```

## Figure5.f) Mean expression of cytokine signaling genes by selection intermediates of the indicated co-receptor status.

```{r,echo=T, eval=T, cache=T, message=F, warning=FALSE, fig.width=16, fig.height=7}

draw_Plots(data_scatter, meta_data_new, 'Il7r')
draw_Plots(data_scatter, meta_data_new, 'Socs1')
draw_Plots(data_scatter, meta_data_new, 'Stat5a')
```

## Figure 6.c) Mean expression of Cd40lg, involved in T cell help, and the cytotoxic T cell marker Prf1 in selection intermediates with distinct co-receptor gene expression.

```{r,echo=T, eval=T, cache=T, message=F, warning=FALSE, fig.width=16, fig.height=7}
draw_Plots(data_scatter, meta_data_new, 'Cd40lg')
draw_Plots(data_scatter, meta_data_new, 'Prf1')

```


## Figure 6.d) Mean expression of H2-K1 and B2m in selection intermediates with distinct co-receptor gene expression.

```{r,echo=T, eval=T, cache=T, message=F, warning=FALSE, fig.width=16, fig.height=7}

draw_Plots(data_scatter, meta_data_new, "H2-K1")
draw_Plots(data_scatter, meta_data_new, 'B2m')

```

## Sup Figure 9.b) The mean expression of the Cd8 lineage genes Itgae and Nkg7 is plotted for the indicated populations, including selection intermediates of the indicated co-receptor gene expression status, in MHC class II-/- thymus.


```{r,echo=T, eval=T, cache=T, message=F, warning=FALSE, fig.width=16, fig.height=7}

Rep1_filtered_rep2 <- subset(WT_Thymocye.integrated, cells = rownames(meta_info[meta_info$celltype != "CD4SP_Immature" &
         ((meta_info$rep=='rep2_KO' & meta_info$celltype=='CD69posDP' & meta_info$nCount_RNA < 1500000 & meta_info$nCount_RNA > 750000) |
         (meta_info$rep=='rep2_KO' & meta_info$celltype!='CD69posDP' & meta_info$nCount_RNA < 1500000 & meta_info$nCount_RNA > 500000))
                ,]))

Rep1_filtered_rep2 <- subset(Rep1_filtered_rep2, cells = rownames(meta_info[
           !((meta_info$celltype=="CD69posDP" | meta_info$celltype=="TCRhiDP" | meta_info$celltype=="CD4+8low") & meta_info$Cd4=="Cd4-" & meta_info$Cd8=="Cd8-")
                ,]))


Rep1_filtered_rep2@meta.data[((Rep1_filtered_rep2@meta.data$celltype=="CD69posDP" | Rep1_filtered_rep2@meta.data$celltype=="TCRhiDP" | Rep1_filtered_rep2@meta.data$celltype=="CD4+8low") & Rep1_filtered_rep2@meta.data$Cd4=="Cd4+" & Rep1_filtered_rep2@meta.data$Cd8=="Cd8+"), 'celltype'] <- "Sel_Intermed_Cd4+Cd8+"

Rep1_filtered_rep2@meta.data[((Rep1_filtered_rep2@meta.data$celltype=="CD69posDP" | Rep1_filtered_rep2@meta.data$celltype=="TCRhiDP" | Rep1_filtered_rep2@meta.data$celltype=="CD4+8low") & Rep1_filtered_rep2@meta.data$Cd4=="Cd4+" & Rep1_filtered_rep2@meta.data$Cd8=="Cd8-"), 'celltype'] <- "Sel_Intermed_Cd4+Cd8-"

Rep1_filtered_rep2@meta.data[((Rep1_filtered_rep2@meta.data$celltype=="CD69posDP" | Rep1_filtered_rep2@meta.data$celltype=="TCRhiDP" | Rep1_filtered_rep2@meta.data$celltype=="CD4+8low") & Rep1_filtered_rep2@meta.data$Cd4=="Cd4-" & Rep1_filtered_rep2@meta.data$Cd8=="Cd8+"), 'celltype'] <- "Sel_Intermed_Cd4-Cd8+"


DefaultAssay(Rep1_filtered_rep2) <- "RNA"
data_scatter <- as.data.frame(t(GetAssayData(Rep1_filtered_rep2,slot='data',assay = "RNA")))
meta_data_new <- Rep1_filtered_rep2@meta.data
meta_data_new$PC_1 <- 0
meta_data_new$PC_1 <- Rep1_filtered_rep2@reductions$pca@cell.embeddings[rownames(meta_data_new),'PC_1']

meta_data_new$Cd4Cd8 <- "NA"
meta_data_new$Cd4Cd8 <- paste0(meta_data_new$Cd4, meta_data_new$Cd8)

meta_data_new$PC1_range <- "-10_to_-5"
meta_data_new[meta_data_new$PC_1 > -5 & meta_data_new$PC_1 < -2.5, "PC1_range" ] <- "-5_to_-2.5"
meta_data_new[meta_data_new$PC_1 > -2.5 & meta_data_new$PC_1 < 0, "PC1_range" ] <- "-2.5_to_0"
meta_data_new[meta_data_new$PC_1 > 0 & meta_data_new$PC_1 < 2.5, "PC1_range" ] <- "0_to_2.5"
meta_data_new[meta_data_new$PC_1 > 2.5 & meta_data_new$PC_1 < 7.5, "PC1_range" ] <- "2.5_to_7.5"

draw_Plots(data_scatter, meta_data_new, 'Itgae')
draw_Plots(data_scatter, meta_data_new, 'Nkg7')

```


## Session Info

```{r Session, eval=T, echo=T}
sessionInfo()

```

